%-------------------------
% David Dellsperger's Full CV
% Author : David Dellsperger
%------------------------
\documentclass[letterpaper,11pt]{article}

\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage[usenames,dvipsnames]{color}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\usepackage[bottom]{footmisc}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule\vspace{-5pt}]

\renewcommand{\labelitemii}{$\circ$}

%-------------------------
% Custom commands

% resume item - short title with description
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

% resume item - short title with description, then tech stack components
\newcommand{\resumeItemWithTech}[3]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}\\
    \textbf{Technology Stack}{: #3 \vspace{-2pt}}
  }
}

% resume positions
\newcommand{\resumePositionListStart}{\begin{itemize}[leftmargin=*,label={}]}
\newcommand{\resumePositionListEnd}{\end{itemize}}
% resume position - company, location, job title, and representative
\newcommand{\resumePosition}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & {\small#4} \\
    \end{tabular*}\vspace{-5pt}
}

% For use when you have a company with multiple job titles over the length of a resume
\newcommand{\resumeCompanyStart}{\vspace{-1pt}\item\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}}
\newcommand{\resumeCompanyEnd}{\end{tabular*}\vspace{-5pt}}
% resume company for multiple job titles per company
\newcommand{\resumeCompany}[2]{
  \textbf{#1} & #2 \\
}

% resume job title for separating multiple job titles within a company
\newcommand{\resumeJobTitle}[2]{
  \textit{\small#1} & {\small#2} \\
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}
\newcommand{\resumeSubItemWithTech}[3]{\resumeItemWithTech{#1}{#2}{#3}\vspace{-4pt}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large David Dellsperger} & Email : \href{mailto:david.dellsperger@gmail.com}{david.dellsperger@gmail.com}\\
  & Mobile : 816-853-1627 \\
\end{tabular*}\vspace{-15pt}

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumePositionListStart

  \resumeCompanyStart
    \resumeCompany{\href{https://snaplogic.com}{SnapLogic}}{Remote - Kansas City, MO}
    \resumeJobTitle{Staff Software Engineer - Snaps}{August 2022 - Present}
    \resumeJobTitle{Senior Software Engineer - Snaps}{February 2021 - July 2022}
  \resumeCompanyEnd
  \resumeItemListStart
    \resumeItem{Deployment Process Improvement}
      {
        Took a process for deploying completed tickets from a month-long task to a week-to-day-long task via JIRA.
        Reduced time from fix to release from nearly 1 month to an average of 1 week.
      }
    \resumeItem{OAuth2 Improvements}
      {
        Added support for generic OAuth2 capabilties for grant types including client credentials, password, and authorization code.
        Hardened the details of the request patterns to align with the full spec of RFC 6749 for web protocols.
      }
    \resumeItem{Authenticated Proxy Support}
      {
        Spent time researching and implemented standard ways to support authenticated proxies across the codebase which are not impacted by the limitations of the JVM and its arguments.
        Focused support for http-based services across multiple http client implementations as well as soap-based services over both apache cxf and apache httpcomponents implementations.
      }
    \resumeItem{Technology Stack}{Java, Maven, MacOS, JIRA, Git, GitHub, Travis CI}
  \resumeItemListEnd

    \resumeCompanyStart
      \resumeCompany{\href{https://cerner.com}{Cerner}}{Kansas City, KS and Kansas City, MO}
      \resumeJobTitle{Senior Software Engineer}{October 2019 - February 2021}
    \resumeCompanyEnd
    \resumeItemListStart
      \resumeItemWithTech{CareDecisions Models}
        {Built and maintained framework for clinical decision support and predictive clinical alerting in Cerner Millennium. Implemented numerous model in the framework including Rehabilitation Acute Care Transfer, Suicide Risk, Acute Myocardial Infarction Readmission, Acute Kidney Injury Risk, Pre-Chronic Kidney Disease Risk, Pediatric Early Warning Score Prime, Febrile Neutropenia Risk, and Tumor Lysis Syndrome Predictor. Added additional clinical attributes, improved run time performance, and overhauled testing.}
        {Java, Drools, Maven, Oracle SQL, JIRA, Git, GitHub, Jenkins}
      \resumeItemWithTech{Rehabilitation Acute Care Transfer}
        {Developed, enhanced, monitored, and supported realtime predictive clinical model for identifying risk of readmission from Acute Care facilities.  Worked directly with client representatives and physicans to gather requirements and enhance the protocol.}
        {Java, Drools, Maven, Oracle SQL, JIRA, Git, GitHub, Jenkins}
    \resumeItemListEnd
    \resumeCompanyStart
      \resumeJobTitle{Associate Senior Software Engineer}{October 2017 - September 2019}
    \resumeCompanyEnd
    \resumeItemListStart
      \resumeItemWithTech{CareProtocols}
        {CareProtocols are point of care utilities designed to be run within Cerner Millennium for clinicians to assist in conforming to workflow-based standard and guidelines. This work consisted of both a fully-embeded solution as well as a remote server impelmentation to increase the development speed of further protocols. Worked directly with client representatives and physicians to gather requirements, build out test case evidence, and enhance the protocols to better work with existing workflows. }
        {Java, Drools, Maven, Spring dependency injection, RESTful Services, Chef (deployment), JIRA, Git, GitHub}
      \resumeItemWithTech{Mentoring}
        {Act as a mentor to new associates hired in engineering assisting with providing feedback on the development process as well as guidance on further development work.}
        {JIRA, Crucible (Code Reviews), Git, GitHub, Jenkins}
    \resumeItemListEnd
    \resumeCompanyStart
      \resumeJobTitle{Software Engineer}{May 2014 - September 2016}
    \resumeCompanyEnd
    \resumeItemListStart
      \resumeItemWithTech{Readmissions Outcome Service}
        {Took over an existing project that executed a predictive model on a hadoop cluster, leveraging full medical records of patients in a batch operation. Made enhancements to the predictive model and corresponding services to support both model runtime and model output serving. Added further model implementations based on provided model designs for further analysis.}
        {Java, Drools, Hadoop MapReduce, Maven, Oracle SQL, Bash, JIRA, Git, GitHub, Jenkins}
    \resumeItemListEnd

    \resumeCompanyStart
      \resumeCompany{University of Iowa College of Engineering}{Iowa City, IA}
      \resumeJobTitle{Head Teaching Assistant}{Semesters: Spring 2012, Fall 2012, Spring 2013, Fall 2014}
      \resumeJobTitle{Teaching Assistant}{Semesters: Spring 2011, Fall 2011}
    \resumeCompanyEnd
    \resumeItemListStart
      \resumeItem{Course - Engineering Problem Solving II}
        {Engineering Problem Solving II is the second core engineering course taken by all engineering students in the College of Engineering. Topics taught include fundamental command-line usage, C programming, MATLAB programming. Semesters had between 160 and 400 students with 8 to 15 other teaching assistants and 2 to 3 professors. }
    \resumeItemListEnd

    \resumePosition
      {\href{http://genome.uiowa.edu/clcg/}{University of Iowa Coordinated Lab for Computational Genomics}}{Iowa City, IA}
      {Graduate Research Assistant}{August 2011 - December 2013}
    \resumeItemListStart
      \resumeItemWithTech{Outcome Prediction in Head and Neck Cancer Patients using Machine Learning Methods}
        {Participated in weekly lab meeting discussing various research taking place in the lab. Worked on research for developing a machine learning algorithm to predict the outcome of head and neck cancer patients prior to treatment using various machine learning techniques.}
        {Java, Python, Weka}
    \resumeItemListEnd

    \resumePosition
      {Bio::Neos}{Coralville, IA}
      {Developer}{May 2011 - August 2011}
    \resumeItemListStart
      \resumeItemWithTech{VCMap}
        {Developed backend code to support additional data sources into the VC Map application as well as fix bugs in the Swing frontend of the VCMap application.  Developed a timing system to determine where latency in loading large datasets was occuring and reduced load time of large variant files by 80\%.}
        {Java, Java Swing (UI), SVN}
    \resumeItemListEnd

  \resumePositionListEnd


%-----------EDUCATION-----------------
\section{Education}
  \resumePositionListStart
    \resumePosition
      {The University of Iowa College of Engineering}{Iowa City, IA}
      {Master of Science in Biomedical Engineering;  GPA: 3.58}{August 2011 - May 2014}
    \resumeItemListStart
      \resumeItem{
          \href{https://iro.uiowa.edu/esploro/outputs/graduate/Outcome-prediction-in-head-and-neck/9983777204002771?institution=01IOWA_INST}{Outcome Prediction in Head and Neck Cancer Patients using Machine Learning Methods}
          \footnote{\url{https://iro.uiowa.edu/esploro/outputs/graduate/Outcome-prediction-in-head-and-neck/9983777204002771?institution=01IOWA_INST}}
        }
        {
          Graduate thesis using various machine learning techniques in order to attempt to predict cancer outcomes in head and neck cacncer patients prior to any treatment taking place.
          This involved multiple poster session presentations and a Masters Thesis defense.
        }
    \resumeItemListEnd
    \resumePosition
      {The University of Iowa College of Engineering}{Iowa City, IA}
      {Bachelor of Engineering in Biomedical Engineering;  GPA: 3.38}{August 2007 - May 2011}
  \resumePositionListEnd


%-----------PROJECTS-----------------
\section{Projects}
  \resumePositionListStart
    \resumeSubItemWithTech{\href{https://github.com/ddellspe/music-bot}{Music Bot}\footnote{https://github.com/ddellspe/music-bot}}
      {Tool to replace Groovy/Rythm within discord. Runs via docker and is configurable via a config file to work with a given set of discord servers.}
      {Maven, Java, GitHub Actions, Docker, Spring Boot, Reactor Core, JUnit Testing}
    \resumeSubItemWithTech{\href{https://anomalyregistration.com}{Anomaly Registration}\footnote{https://anomalyregistration.com} (no longer active)}
      {Tool used by the Ingress Resistance in the Americas, Asia, and Australia in order to collect participant information for vetting and organization for Ingress Anomaly events.}
      {Python, Google App Engine, Javascript, Git, GitLab, Bash}
  \resumePositionListEnd


%--------PROGRAMMING EXPERIENCE------------
\section{Programming Experience}
  \resumePositionListStart
    \item{
      \textbf{Languages}{: Java, Python, SQL, JavaScript, Bash}
    }\vspace{-8pt}
    \item{
      \textbf{Technologies and Tools}{: Drools, Google App Engine, Docker, Chef, Git, Jenkins, GitHub}
    }\vspace{-8pt}
  \resumePositionListEnd
%-------------------------------------------
\end{document}
