\resumeCompanyStart
    \resumeCompany{\href{https://cerner.com}{Cerner}}{Kansas City, KS and Kansas City, MO}
    \resumeJobTitle{Senior Software Engineer}{October 2019 - February 2021}
\resumeCompanyEnd

\resumeItemListStart
    \resumeItemWithTech{CareDecisions Models}
    {Built and maintained framework for clinical decision support and predictive clinical alerting in Cerner Millennium. Implemented numerous model in the framework including Rehabilitation Acute Care Transfer, Suicide Risk, Acute Myocardial Infarction Readmission, Acute Kidney Injury Risk, Pre-Chronic Kidney Disease Risk, Pediatric Early Warning Score Prime, Febrile Neutropenia Risk, and Tumor Lysis Syndrome Predictor. Added additional clinical attributes, improved run time performance, and overhauled testing.}
    {Java, Drools, Maven, Oracle SQL, Jira, Git, GitHub, Jenkins}
    \resumeItemWithTech{Rehabilitation Acute Care Transfer}
    {Developed, enhanced, monitored, and supported realtime predictive clinical model for identifying risk of readmission from Acute Care facilities.  Worked directly with client representatives and physicans to gather requirements and enhance the protocol.}
    {Java, Drools, Maven, Oracle SQL, Jira, Git, GitHub, Jenkins}
\resumeItemListEnd

\resumeCompanyStart
    \resumeJobTitle{Associate Senior Software Engineer}{October 2017 - September 2019}
\resumeCompanyEnd
\resumeItemListStart
    \resumeItemWithTech{CareProtocols}
    {CareProtocols are point of care utilities designed to be run within Cerner Millennium for clinicians to assist in conforming to workflow-based standard and guidelines. This work consisted of both a fully-embeded solution as well as a remote server impelmentation to increase the development speed of further protocols. Worked directly with client representatives and physicians to gather requirements, build out test case evidence, and enhance the protocols to better work with existing workflows. }
    {Java, Drools, Maven, Spring dependency injection, RESTful Services, Chef (deployment), Jira, Git, GitHub}
    \resumeItemWithTech{Mentoring}
    {Act as a mentor to new associates hired in engineering assisting with providing feedback on the development process as well as guidance on further development work.}
    {Jira, Crucible (Code Reviews), Git, GitHub, Jenkins}
\resumeItemListEnd

\resumeCompanyStart
    \resumeJobTitle{Software Engineer}{May 2014 - September 2016}
\resumeCompanyEnd
\resumeItemListStart
    \resumeItemWithTech{Readmissions Outcome Service}
    {Took over an existing project that executed a predictive model on a hadoop cluster, leveraging full medical records of patients in a batch operation. Made enhancements to the predictive model and corresponding services to support both model runtime and model output serving. Added further model implementations based on provided model designs for further analysis.}
    {Java, Drools, Hadoop MapReduce, Maven, Oracle SQL, Bash, Jira, Git, GitHub, Jenkins}
\resumeItemListEnd