\resumeCompanyStart
    \resumeCompany{\href{https://snaplogic.com}{SnapLogic}}{Remote - Kansas City, MO}
    \resumeJobTitle{Staff Software Engineer - Snaps}{August 2022 - Present}
\resumeCompanyEnd
\resumeItemListStart
    \resumeItem{Pipeline Cache}
    {
        Worked across multiple teams in order to assist in design, development, and training for the Pipeline Cache feature for the SnapLogic Platform.
        Worked with a tight deadline to deliver a rich new feature to support further capabilties that were previously difficult to accomplish.
    }
    \resumeItem{SWAT Lead}
    {
        Lead efforts for tier 3 support via engineering, investigating reported bugs to determine if items were configuration updates or bugs in code.
        Reached across both the Snap team as well as Platform team in order to triage, identify, and fix code defects and update documentation accordingly when required.
    }
    \resumeItem{Development Process Improvement}
    {
        Lead the direction of new Jira workflows in coordination with documented development procedures in order to help to refine and address process gaps.
        Worked across multiple affected parties including Product, Documentation, and QA to address all concerns.
    }
    \resumeItem{Deployment Process Improvement}
    {
        Took a process for deploying completed tickets from a month-long task to a week-to-day-long task via Jira.
        Reduced time from fix to release from nearly 1 month to an average of 1 week.
    }
\resumeItemListEnd
\resumeCompanyStart
    \resumeJobTitle{Senior Software Engineer - Snaps}{February 2021 - July 2022}
\resumeCompanyEnd
\resumeItemListStart
    \resumeItem{OAuth2 Improvements}
    {
        Added support for generic OAuth2 capabilties for grant types including client credentials, password, and authorization code.
        Hardened the details of the request patterns to align with the full spec of RFC 6749 for web protocols.
    }
    \resumeItem{Authenticated Proxy Support}
    {
        Spent time researching and implemented standard ways to support authenticated proxies across the codebase which are not impacted by the limitations of the JVM and its arguments.
        Focused support for http-based services across multiple http client implementations as well as soap-based services over both apache cxf and apache httpcomponents implementations.
    }
    \resumeItem{Technology Stack}{Java, Maven, MacOS, Jira, Git, GitHub, Travis CI}
\resumeItemListEnd