%-----------EXPERIENCE-----------%
\section{Experience}
\resumeSubHeadingListStart

    \resumeSubheading
    {\href{https://vannevarlabs.com/}{Vannevar Labs}}{July 2025 - Present}
    {Software Engineer - L4}{Palo Alto, CA (Remote in Kansas City, MO)}
    \resumeItemListStart
        \resumeItem{\textbf{Platform ML} - Led the design and development of an LLM Proxy that coordinates between multiple LLM providers and different APIs. }
    \resumeItemListEnd

    \resumeSubheading
    {\href{https://snaplogic.com}{SnapLogic}}{October 2024 - July 2025}
    {Senior Staff Software Engineer}{San Mateo, CA (Remote in Kansas City, MO)}
    \resumeItemListStart
        \resumeItem{\textbf{AgentCreator} - led the architecture, design, and development process with a team of 6 engineers, 3 quality engineering members to deliver new features, bug fixes, and coordinating with the salesteam, marketing, and customer success teams to provide customers up-to-date details as new features and capabilities are released.}
        \resumeItem{\textbf{GenAI Escape Room} - Conceptualized, designed, and developed an \href{https://escapegenai.com}{escape room-based training tool} to assist in training customers and pre-sales on the features and supported capabilities of the AgentCreator product. Added support to automatically deploy via a Teraform script for pre-sales to deliver the training to customers as desired.  Delivered this training in multiple cross-functional training sessions for customers, partners, profefessional services engineers, and sales engineers to enable the discovery of AgentCreator as a product in a variety of use cases. }
    \resumeItemListEnd

    \resumeSubheading
    {\href{https://snaplogic.com}{SnapLogic}}{Aug 2022 - September 2024}
    {Staff Software Engineer}{San Mateo, CA (Remote in Kansas City, MO)}
    \resumeItemListStart
        \resumeItem{\textbf{GenAI App Builder} - Led a four-intern team through the research of integrationg LLMs into the landscape of the SnapLogic Designer. I then led the design and initial release development of the SnapLogic GenAI App Builder product (now called AgentCreator), opening up integrations with OpenAI, Azure OpenAI, and Pinecone. Formally interviewed and hired 3 of the interns full-time to start after the initial release of the product.}
        \resumeItem{\textbf{SWAT Process Improvement} - Led the initiative to reduce the tier 3 backlog of customer-reported issues, resulting in reducing the average time to fix bugs from 40+ days to 5 days.  Led a rotating group of 4-6 engineers from a 20-engineer team to triage tickets and address concerns including code reviews, issue reproduction, and customer outreach as necessary.}
        \resumeItem{\textbf{Development Process Improvement} - Implemented SDLC improvements to support more efficient planning and delivery of both new product features and bug fixes. Worked with product managers, engineering leaders, and quality engineering leaders to align on a process that supported all necessary workflow considerations to track a story, and bug from inception to release to production.}
        \resumeItem{\textbf{Cache Pipelines} - Lead the design and development effort across multiple teams to impelement a new platform feature to support caching data for a pipeline-global lookup of properties.}
    \resumeItemListEnd

    \resumeSubheading
    {\href{https://snaplogic.com}{SnapLogic}}{Feb 2021 - July 2022}
    {Senior Software Engineer}{San Mateo, CA (Remote in Kansas City, MO)}
    \resumeItemListStart
        \resumeItem{\textbf{Deployment Process Improvement} - Implemented a process to efficiently track and manage the deployment of fixes and features, reducing the time from resolution to availability from one week to one day.}
        \resumeItem{\textbf{OAuth2 Improvements} - Added support for generic OAuth2 capabilities for grant types including client credentials, password, and authorization code, aligning with RFC 6749.}
        \resumeItem{\textbf{Authenticated Proxy Support} - Researched and implemented standard approaches to support authenticated proxies across the codebase.}
    \resumeItemListEnd
    
    \resumeSubheading
    {\href{https://engineering.cerner.com/}{Cerner}}{Oct 2019 - Feb 2021}
    {Senior Software Engineer}{Kansas City, MO}
    \resumeItemListStart
        \resumeItem{\textbf{CareDecisions Models} - Developed and maintained framework for clinical decision support and predictive clinical alerting in Cerner Millennium. Collaborated with external teams to work on enhancing support for new data capture for processing support for the Discern Ontology-based data.}
        \resumeItem{\textbf{Rehabilitation Acute Care Transfer} - Developed, enhanced, monitored, and supported real-time predictive clinical model for identifying risk of readmission to acute care facilities.}
    \resumeItemListEnd

    \resumeSubheading
    {\href{https://engineering.cerner.com/}{Cerner}}{Oct 2016 - Sep 2019}
    {Associate Senior Software Engineer}{Kansas City, KS}
    \resumeItemListStart
        \resumeItem{\textbf{CareProtocols} - Developed and maintained point of care utilities designed to be run within Cerner Millennium for clinicians to assist in conforming to workflow-based processes.}
        \resumeItem{\textbf{Mentoring} - Mentored new associates in the engineering department by providing feedback on the development process and guiding development work.}
    \resumeItemListEnd

    \resumeSubheading
    {\href{https://engineering.cerner.com/}{Cerner}}{May 2014 - Sep 2016}
    {Software Engineer}{Kansas City, KS}
    \resumeItemListStart
        \resumeItem{\textbf{Readmissions Outcome Service} - Maintained a project that executed predictive models on a Hadoop cluster, leveraging the full medical records of patients in a batch operation.}
    \resumeItemListEnd

    % \resumeSubheading
    % {University of Iowa College of Engineering}{January 2012 - May 2014}
    % {Head Teaching Assistant}{Iowa City, IA}
    % \resumeItemListStart
    %     \resumeItem{Engineering Problem Solving II - Worked as a Head Teaching Assistant, teaching students introductory C and MATLAB programming; hosting office hours, grading homework, proctoring exams, and writing exams.}
    %     \resumeItem{Scheduled and organized teaching assistants for office hours, homework grading rotations, and exam proctoring.}
    % \resumeItemListEnd

    % \resumeSubheading
    % {\href{http://genome.uiowa.edu/clcg/}{University of Iowa Coordinated Lab for Computational Genomics}}{August 2011 - December 2013}
    % {Graduate Research Assistant}{Iowa City, IA}
    % \resumeItemListStart
    %     \resumeItem{Participated in weekly lab meeting discussing various research taking place in the lab.}
    %     \resumeItem{Thesis Work - Outcome Prediction in Head and Neck Cancer Patients using Machine Learning Methods}
    % \resumeItemListEnd

    % \resumeSubheading
    % {\href{https://bioneos.com/}{Bio::Neos}}{May 2011 - August 2011}
    % {Developer}{Coralville, IA}
    % \resumeItemListStart
    %     \resumeItem{VCMap - Helped with bugfixes and UI development and performance.}
    % \resumeItemListEnd

    % \resumeSubheading
    % {University of Iowa College of Engineering}{January 2011 - December 2011}
    % {Teaching Assistant}{Iowa City, IA}
    % \resumeItemListStart
    %     \resumeItem{Engineering Problem Solving II - Worked as a Teaching Assistant, teaching students introductory C and MATLAB programming; hosting office hours, grading homework, proctoring exams, and writing exams.}
    % \resumeItemListEnd

\resumeSubHeadingListEnd