%-----------PROJECTS-----------%
\section{Projects}
\resumeSubHeadingListStart

    \resumeProjectHeading
    {\textbf{GenAI App Builder} $|$ \emph{Java, Maven, Generative AI, REST, Mentoring, Management}}    {}
    \resumeItemListStart
        \resumeItem{Led the development of integrations with OpenAI, Azure OpenAI and Pinecone services to run Generative AI APIs via low-code/no-code interfaces.}
        \resumeItem{Designed and developed the initial integration interfaces that are leveraged after enhancement work to support connections to major LLM providers and Vector DBs.}
        \resumeItem{Defined and scoped work for a team of six engineers to continue development after initial release supporting expanded functionality and vendor-specific features.}
        \resumeItem{Work directly with customers to facilitate the production rollout of multiple use cases leveraging the initial designs of the GenAI App Builder solution.}
    \resumeItemListEnd

    \resumeProjectHeading
    {\textbf{SWAT Team Process Improvement} $|$ \emph{Java, Maven, REST, SDLC, Process Improvement}}    {}
    \resumeItemListStart
        \resumeItem{Led the development processs changes to support a twelve-engineer team in reducing the support and feature backlogs to addresss customer needs in a more timely manner.}
        \resumeItem{Reduced mean time to resolution of customer support requests from 90 days down to 30 days on average with an average triage response time of 2 business days.}
        \resumeItem{Reduced the customer support backlog from over 40 items in backlog to 5 items in the backlog with a five-engineer team ready to transition to new tickets immediately.}
    \resumeItemListEnd

    \resumeProjectHeading
    {\textbf{Cache Pipelines} $|$ \emph{Java, Maven, Memory Management, Cross-Team Collaboration}}    {}
    \resumeItemListStart
        \resumeItem{Worked across multiple teams in order to assist in design, development, and training for the Pipeline Cache feature for the SnapLogic Platform.}
        \resumeItem{Worked with a tight deadline to deliver a rich new feature to support further capabilties that were previously difficult to accomplish.}
    \resumeItemListEnd

    \resumeProjectHeading
    {\textbf{\href{https://github.com/ddellspe/music-bot}{Music Bot}} $|$ \emph{Java, Spring Boot, Maven, Github Actions, Docker, Reactor Core, JUnit Testing}} {}
    \resumeItemListStart
        \resumeItem{Tool to replace Groovy/Rythm within discord. Runs via docker and is configurable via a config file to work with a given set of discord servers.}
    \resumeItemListEnd

    \resumeProjectHeading
    {\textbf{Rehabilitation Acute Care Transfer Model} $|$ \emph{Java, Maven, Drools, Oracle SQL, Machine Learning Implementation}} {}
    \resumeItemListStart
        \resumeItem{Developed, enhanced, monitored, and supported realtime predictive clinical model for identifying risk of readmission from Acute Care facilities.}
        \resumeItem{Worked directly with client representatives and physicans to gather requirements and enhance the protocol.}
    \resumeItemListEnd

\resumeSubHeadingListEnd